A Typed Programmatic Interface to Contracts on the Blockchain

### 2021-06-08 papers/execution-model/APLAS 2021/paper.tex
Add files via upload

%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of Freiburg, Germany \\
\email{\{doanha,thiemann\}@informatik.uni-freiburg.de}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
  Smart contract applications on the block chain can only reach their full potential if
  they can be integrated with traditional software systems. Invoking
  contracts and observing the state of the blockchain requires a
  programmatic interface. We propose a typed API for this
  purpose and establish some properties of the combined
  system. Specifically, we provide an execution model that
  enables us to prove type-safe interaction between programs and the 
  blockchain. We establish further properties of the model that
  give rise to requirements on the API. A prototype of the interface
  is implemented in OCaml for the Tezos blockchain.

@@

\begin{itemize}
\item An operational semantics for functional programs running
  alongside smart contracts in a blockchain. 
\item Established various properties of the combined system withs
  proofs in upcoming techreport.
\item An implementation of a low-level OCaml-API to the Tezos
  blockchain, which corresponds to the operational semantics.\footnote{%
    Available at \url{https://github.com/tezos-project/Tezos-Ocaml-API}.}
\end{itemize}

@@

Suppose you want to run an auction on the blockchain using a smart
contract. Once to the contract is deployed, the
auction is open for bidding, but it should be closed after 48 hours. Such a timeout is a typical task for an oracle. Rather than
trusting a generic oracle, you prefer to roll your own mechanism that reliably closes the auction
after 48 hours have passed. So you want to write a program to do so.

>>>>

%
\authorrunning{F. Author et al.}
% First names are abbreviated in the running head.
% If there are more than two authors, 'et al.' is used.
%
\institute{University of Freiburg, Germany \\
\email{\{doanha,thiemann\}@informatik.uni-freiburg.de}
}
%
\maketitle              % typeset the header of the contribution
%
\begin{abstract}
  Smart contract applications on the blockchain can only reach their full potential if
  they can be integrated with traditional software systems. Invoking
  contracts and observing the state of the blockchain requires a
  programmatic interface. We propose a typed API for this
  purpose and establish some properties of the combined
  system. Specifically, we provide an execution model that
  enables us to prove type-safe interaction between programs and the 
  blockchain. We establish further properties of the model that
  give rise to requirements on the API. A prototype of the interface
  is implemented in OCaml for the Tezos blockchain.

@@

\begin{itemize}
\item An operational semantics for functional programs running
  alongside smart contracts in a blockchain. 
\item Established various properties of the combined system with
  proofs in upcoming techreport.
\item An implementation of a low-level OCaml-API to the Tezos
  blockchain, which corresponds to the operational semantics.\footnote{%
    Available at \url{https://github.com/tezos-project/Tezos-Ocaml-API}.}
\end{itemize}

@@

Suppose you want to run an auction on the blockchain using a smart
contract. Once the contract is deployed, the
auction is open for bidding, but it should be closed after 48 hours. Such a timeout is a typical task for an oracle. Rather than
trusting a generic oracle, you prefer to roll your own mechanism that reliably closes the auction
after 48 hours have passed. So you want to write a program to do so.
